---
title: "R Notebook"
output: html_notebook
---

```{r}
HIRN_data <- readRDS("H:/LAB 20 IIT K/HIRN-PANC DB/HIRN updated/Working rds/HIRN seurat processed and annotated wo juvenile JT.rds")

HIRN_data$old_names <- HIRN_data$cellchat_states.detailed


HIRN_data <- SetIdent(HIRN_data,value = HIRN_data$old_names)


unique(HIRN_data$old_names)

saveRDS(HIRN_data, "H:/LAB 20 IIT K/HIRN-PANC DB/HIRN updated/Working rds/HIRN seurat processed and annotated wo juvenile JT.rds")

D1 <- DimPlot(HIRN_data)
ggsave(plot = D1, filename = "HIRN_data Dimplot detailed.tiff", path = "H:/LAB 20 IIT K/M.TECH THESIS/HIRN Data/Sheets/Hs-First fig/",height = 5, width = 10, device = "tiff", dpi = 600)

D2 <- DimPlot(HIRN_data, split.by = "condition")+NoLegend()
ggsave(plot = D2, filename = "HIRN_data Dimplot split.by.cond detailed.tiff", path = "H:/LAB 20 IIT K/M.TECH THESIS/HIRN Data/Sheets/Hs-First fig/",height = 5, width = 15, device = "tiff", dpi = 600)

D3 <- DimPlot(HIRN_data, label = T, repel = T, label.size = 2.5)
ggsave(plot = D3, filename = "HIRN_data Dimplot labeled detailed.tiff", path = "H:/LAB 20 IIT K/M.TECH THESIS/HIRN Data/Sheets/Hs-First fig/",height = 5, width = 10, device = "tiff", dpi = 600)
```

```{r}
HIRN_data@meta.data$cellchat_states.detailed <- 0

HIRN_data@meta.data[HIRN_data@meta.data$old_names %in% "Hs-Alpha 1", "cellchat_states.detailed"] <- "Hs-Alpha 1"
HIRN_data@meta.data[HIRN_data@meta.data$old_names %in% "Hs-Alpha 2", "cellchat_states.detailed"] <- "Hs-Alpha 2"
HIRN_data@meta.data[HIRN_data@meta.data$old_names %in% "Hs-Beta 1", "cellchat_states.detailed"] <- "Hs-Beta 1"
HIRN_data@meta.data[HIRN_data@meta.data$old_names %in% "Hs-Beta 2", "cellchat_states.detailed"] <- "Hs-Beta 2"
HIRN_data@meta.data[HIRN_data@meta.data$old_names %in% "Hs-Beta 3", "cellchat_states.detailed"] <- "Hs-Beta 3"
HIRN_data@meta.data[HIRN_data@meta.data$old_names %in% "Hs-Delta 1", "cellchat_states.detailed"] <- "Hs-Delta 1"
HIRN_data@meta.data[HIRN_data@meta.data$old_names %in% "Hs-Delta 2", "cellchat_states.detailed"] <- "Hs-Delta 2"
HIRN_data@meta.data[HIRN_data@meta.data$old_names %in% "Hs-Gamma", "cellchat_states.detailed"] <- "Hs-Gamma"
HIRN_data@meta.data[HIRN_data@meta.data$old_names %in% "Hs-Acinar", "cellchat_states.detailed"] <- "Hs-Acinar"
HIRN_data@meta.data[HIRN_data@meta.data$old_names %in% "Hs-Activated PSCs", "cellchat_states.detailed"] <- "Hs-Activated PSCs"
HIRN_data@meta.data[HIRN_data@meta.data$old_names %in% "Hs-Quiescent PSCs", "cellchat_states.detailed"] <- "Hs-Quiescent PSCs"
HIRN_data@meta.data[HIRN_data@meta.data$old_names %in% "Hs-PDCs", "cellchat_states.detailed"] <- "Hs-PDCs"
HIRN_data@meta.data[HIRN_data@meta.data$old_names %in% "Hs-Endothelial 1", "cellchat_states.detailed"] <- "Hs-Metabolically active ECs"
HIRN_data@meta.data[HIRN_data@meta.data$old_names %in% "Hs-Endothelial 2", "cellchat_states.detailed"] <- "Hs-Vascular ECs"
HIRN_data@meta.data[HIRN_data@meta.data$old_names %in% "Hs-Endothelial 3", "cellchat_states.detailed"] <- "Hs-Proinflammatory ECs"
HIRN_data@meta.data[HIRN_data@meta.data$old_names %in% "Hs-Endothelial 4", "cellchat_states.detailed"] <- "Hs-Immune regulatory ECs"
HIRN_data@meta.data[HIRN_data@meta.data$old_names %in% "Hs-Immune 1", "cellchat_states.detailed"] <- "Hs-Granulocytes"
HIRN_data@meta.data[HIRN_data@meta.data$old_names %in% "Hs-Immune 2", "cellchat_states.detailed"] <- "Hs-Macrophages"
HIRN_data@meta.data[HIRN_data@meta.data$old_names %in% "Hs-Immune 3", "cellchat_states.detailed"] <- "Hs-APCs"
HIRN_data@meta.data[HIRN_data@meta.data$old_names %in% "Hs-Immune 4", "cellchat_states.detailed"] <- "Hs-T cells"
HIRN_data@meta.data[HIRN_data@meta.data$old_names %in% "Hs-Immune 4", "cellchat_states.detailed"] <- "Hs-T cells"
HIRN_data@meta.data[HIRN_data@meta.data$old_names %in% NA, "cellchat_states.detailed"] <- "Hs-Unclassified"


HIRN_data<-SetIdent(HIRN_data, value = HIRN_data$cellchat_states.detailed)

 levels(HIRN_data) <- c( "Hs-Beta 1", "Hs-Beta 2", "Hs-Beta 3", "Hs-Alpha 1", "Hs-Alpha 2", "Hs-Delta 1", "Hs-Delta 2", "Hs-Gamma", "Hs-Acinar","Hs-PDCs", "Hs-Activated PSCs", "Hs-Quiescent PSCs", "Hs-Vascular ECs", "Hs-Metabolically active ECs", "Hs-Proinflammatory ECs", "Hs-Immune regulatory ECs", "Hs-T cells","Hs-Granulocytes","Hs-Macrophages", "Hs-APCs", "Hs-Unclassified")

HIRN_data$cellchat_states.detailed.condition <- paste0(HIRN_data$cellchat_states.detailed,"_",HIRN_data$condition)

unique(HIRN_data$cellchat_states.detailed.condition)
```


library(CellChat)
cellchat <- readRDS("H:/LAB 20 IIT K/HIRN-PANC DB/HIRN updated/Working rds/HIRN_cellchat_states.detailed.rds")

```{r}
library(CellChat)
cellchat <- readRDS("H:/LAB 20 IIT K/HIRN-PANC DB/HIRN updated/Working rds/HIRN_cellchat_states.detailed.rds")

cellchat@meta
```

####################### Changing labels in cellchat ################################################
Hi @ruohuchengxhe , you should do it levels(cellchat@meta$labels)[levels(cellchat@meta$labels) =='Mast cells' ] <- 'Mc 4' cellchat <- setIdent(cellchat, ident.use = "cell_type") # set "cell_type" as default cell identity

```{r}
levels(cellchat@meta$subtype2_detailed)[levels(cellchat@meta$subtype2_detailed) =="Hs-Alpha 1" ] <- "Hs-Alpha 1"
levels(cellchat@meta$subtype2_detailed)[levels(cellchat@meta$subtype2_detailed) =="Hs-Alpha 2" ] <- "Hs-Alpha 2"
levels(cellchat@meta$subtype2_detailed)[levels(cellchat@meta$subtype2_detailed) =="Hs-Beta 1" ] <- "Hs-Beta 1"
levels(cellchat@meta$subtype2_detailed)[levels(cellchat@meta$subtype2_detailed) =="Hs-Beta 2" ] <- "Hs-Beta 2"
levels(cellchat@meta$subtype2_detailed)[levels(cellchat@meta$subtype2_detailed) =="Hs-Delta 1" ] <- "Hs-Delta 1"
levels(cellchat@meta$subtype2_detailed)[levels(cellchat@meta$subtype2_detailed) =="Hs-Delta 2" ] <- "Hs-Delta 2"
levels(cellchat@meta$subtype2_detailed)[levels(cellchat@meta$subtype2_detailed) =="Hs-Acinar" ] <- "Hs-Acinar"
levels(cellchat@meta$subtype2_detailed)[levels(cellchat@meta$subtype2_detailed) =="Hs-Activated PSCs" ] <- "Hs-Activated PSCs"
levels(cellchat@meta$subtype2_detailed)[levels(cellchat@meta$subtype2_detailed) =="Hs-Quiescent PSCs" ] <- "Hs-Quiescent PSCs"
levels(cellchat@meta$subtype2_detailed)[levels(cellchat@meta$subtype2_detailed) =="Hs-PDCs" ] <- "Hs-PDCs"
levels(cellchat@meta$subtype2_detailed)[levels(cellchat@meta$subtype2_detailed) =="Hs-Endothelial 1" ] <- "Hs-Metabolically active ECs"
levels(cellchat@meta$subtype2_detailed)[levels(cellchat@meta$subtype2_detailed) =="Hs-Endothelial 2" ] <- "Hs-Vascular ECs"
levels(cellchat@meta$subtype2_detailed)[levels(cellchat@meta$subtype2_detailed) =="Hs-Endothelial 3" ] <- "Hs-Proinflammatory ECs"
levels(cellchat@meta$subtype2_detailed)[levels(cellchat@meta$subtype2_detailed) =="Hs-Endothelial 4" ] <- "Hs-Immune regulatory ECs"
levels(cellchat@meta$subtype2_detailed)[levels(cellchat@meta$subtype2_detailed) =="Hs-Immune 1" ] <- "Hs-Granulocytes"
levels(cellchat@meta$subtype2_detailed)[levels(cellchat@meta$subtype2_detailed) =="Hs-Immune 2" ] <- "Hs-Macrophages"
levels(cellchat@meta$subtype2_detailed)[levels(cellchat@meta$subtype2_detailed) =="Hs-Immune 3" ] <- "Hs-APCs"
levels(cellchat@meta$subtype2_detailed)[levels(cellchat@meta$subtype2_detailed) =="Hs-Immune 4" ] <- "Hs-T cells"

cellchat <- setIdent(cellchat, ident.use = "subtype2_detailed")
```
```{r}
data.input <- cellchat@data

```

```{r}
cellchat <- computeCommunProb(cellchat)

cellchat <- filterCommunication(cellchat, min.cells = 10)
cellchat <- computeCommunProbPathway(cellchat)
cellchat <- aggregateNet(cellchat)

```
```{r}
groupSize <- as.numeric(table(cellchat@idents))
par(mfrow = c(1,2), xpd=TRUE)
netVisual_circle(cellchat@net$count, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Number of interactions")
netVisual_circle(cellchat@net$weight, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Interaction weights/strength") 
```



```{r}
cellchat <- setIdent(cellchat, ident.use = "subtype2_detailed")
cellchat@meta
```

```{r}
cellchat@meta$old_names <- cellchat@meta$subtype2_detailed 

cellchat@meta$subtype2_detailed <- 0

cellchat@meta[cellchat@meta$old_names %in% "Hs-Alpha 1", "subtype2_detailed"] <- "Hs-Alpha 1"
cellchat@meta[cellchat@meta$old_names %in% "Hs-Alpha 2", "subtype2_detailed"] <- "Hs-Alpha 2"
cellchat@meta[cellchat@meta$old_names %in% "Hs-Beta 1", "subtype2_detailed"] <- "Hs-Beta 1"
cellchat@meta[cellchat@meta$old_names %in% "Hs-Beta 2", "subtype2_detailed"] <- "Hs-Beta 2"
cellchat@meta[cellchat@meta$old_names %in% "Hs-Beta 3", "subtype2_detailed"] <- "Hs-Beta 3"
cellchat@meta[cellchat@meta$old_names %in% "Hs-Delta 1", "subtype2_detailed"] <- "Hs-Delta 1"
cellchat@meta[cellchat@meta$old_names %in% "Hs-Delta 2", "subtype2_detailed"] <- "Hs-Delta 2"
cellchat@meta[cellchat@meta$old_names %in% "Hs-Acinar", "subtype2_detailed"] <- "Hs-Acinar"
cellchat@meta[cellchat@meta$old_names %in% "Hs-Activated PSCs", "subtype2_detailed"] <- "Hs-Activated PSCs"
cellchat@meta[cellchat@meta$old_names %in% "Hs-Quiescent PSCs", "subtype2_detailed"] <- "Hs-Quiescent PSCs"
cellchat@meta[cellchat@meta$old_names %in% "Hs-PDCs", "subtype2_detailed"] <- "Hs-PDCs"
cellchat@meta[cellchat@meta$old_names %in% "Hs-Endothelial 1", "subtype2_detailed"] <- "Hs-Metabolically active ECs"
cellchat@meta[cellchat@meta$old_names %in% "Hs-Endothelial 2", "subtype2_detailed"] <- "Hs-Vascular ECs"
cellchat@meta[cellchat@meta$old_names %in% "Hs-Endothelial 3", "subtype2_detailed"] <- "Hs-Proinflammatory ECs"
cellchat@meta[cellchat@meta$old_names %in% "Hs-Endothelial 4", "subtype2_detailed"] <- "Hs-Immune regulatory ECs"
cellchat@meta[cellchat@meta$old_names %in% "Hs-Immune 1", "subtype2_detailed"] <- "Hs-Granulocytes"
cellchat@meta[cellchat@meta$old_names %in% "Hs-Immune 2", "subtype2_detailed"] <- "Hs-Macrophages"
cellchat@meta[cellchat@meta$old_names %in% "Hs-Immune 3", "subtype2_detailed"] <- "Hs-APCs"
cellchat@meta[cellchat@meta$old_names %in% "Hs-Immune 4", "subtype2_detailed"] <- "Hs-T cells"

unique(cellchat@meta$subtype2_detailed)

cellchat@meta$subtype2_condition <- paste0(cellchat@meta$subtype2, "_", cellchat@meta$condition)
```











#####################################################################






```{r}
HIRN_data <- SetIdent(HIRN_data, value = HIRN_data$cellchat_states.detailed)

data.input <- GetAssayData(HIRN_data, assay = "RNA", slot = "data") 

labels <- Idents(HIRN_data)
meta <- data.frame(group = labels, row.names = names(labels)) # create a dataframe of the cell labels
colnames(meta)[1] <- "labels"

cellchat <- createCellChat(object = data.input, meta = meta, group.by = "labels")

cellchat <- setIdent(cellchat, ident.use = "labels") # set "labels" as default cell identity
levels(cellchat@idents) <- c( "Hs-Beta 1", "Hs-Beta 2", "Hs-Beta 3", "Hs-Alpha 1", "Hs-Alpha 2", "Hs-Delta 1", "Hs-Delta 2", "Hs-Gamma", "Hs-Acinar","Hs-PDCs", "Hs-Activated PSCs", "Hs-Quiescent PSCs", "Hs-Vascular ECs", "Hs-Metabolically active ECs", "Hs-Proinflammatory ECs", "Hs-Immune regulatory ECs", "Hs-T cells","Hs-Granulocytes","Hs-Macrophages", "Hs-APCs", "Hs-Unclassified") # show factor levels of the cell labels
#groupSize <- as.numeric(table(cellchat@idents)) # number of cells in each cell group
CellChatDB <- CellChatDB.human # use CellChatDB.mouse if running on mouse data

CellChatDB.use <- CellChatDB # simply use the default CellChatDB
cellchat@DB <- CellChatDB.use
cellchat <- subsetData(cellchat) # This step is necessary even if using the whole database
future::plan("multiprocess", workers = 4) # do parallel
cellchat <- identifyOverExpressedGenes(cellchat)
cellchat <- identifyOverExpressedInteractions(cellchat)
cellchat <- computeCommunProb(cellchat)
cellchat <- filterCommunication(cellchat, min.cells = 10)
cellchat <- computeCommunProbPathway(cellchat)
cellchat <- aggregateNet(cellchat)
cellchat <- netAnalysis_computeCentrality(cellchat, slot.name = "netP") 

saveRDS(cellchat, "H:/LAB 20 IIT K/HIRN-PANC DB/HIRN updated/Working rds/HIRN_cellchat_states.detailed JT.rds")
```

```{r}
groupSize <- as.numeric(table(cellchat@idents))
par(mfrow = c(1,2), xpd=TRUE)

netVisual_circle(cellchat@net$count, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Number of interactions", top = 0.40)

netVisual_circle(cellchat@net$weight, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Interaction weights/strength", top = 0.40)

```


```{r}
library(NMF)
library(ggalluvial)

```


```{r}
HIRN_data <- SetIdent(HIRN_data, value = HIRN_data$cellchat_states.detailed)
HIRN_data <- subset(HIRN_data, cellchat_states.detailed != "Hs-Unclassified")


HIRN_data <- SetIdent(HIRN_data, value = HIRN_data$cellchat_states.detailed.condition)

data.input <- GetAssayData(HIRN_data, assay = "RNA", slot = "data") 

labels <- Idents(HIRN_data)
meta <- data.frame(group = labels, row.names = names(labels)) # create a dataframe of the cell labels
colnames(meta)[1] <- "labels"

cellchat <- createCellChat(object = data.input, meta = meta, group.by = "labels")

cellchat <- setIdent(cellchat, ident.use = "labels") # set "labels" as default cell identity
 # show factor levels of the cell labels 



#groupSize <- as.numeric(table(cellchat@idents)) # number of cells in each cell group
CellChatDB <- CellChatDB.human # use CellChatDB.mouse if running on mouse data

CellChatDB.use <- CellChatDB # simply use the default CellChatDB
cellchat@DB <- CellChatDB.use
cellchat <- subsetData(cellchat) # This step is necessary even if using the whole database
future::plan("multiprocess", workers = 4) # do parallel
cellchat <- identifyOverExpressedGenes(cellchat)
cellchat <- identifyOverExpressedInteractions(cellchat)

levels(cellchat@idents) <- unique(cellchat@meta$labels)

cellchat <- computeCommunProb(cellchat)

cellchat  <- setIdent(cellchat, ident.use = "labels", levels = levels_ordered)


cellchat <- filterCommunication(cellchat, min.cells = 10)
cellchat <- computeCommunProbPathway(cellchat)
cellchat <- aggregateNet(cellchat)
cellchat <- netAnalysis_computeCentrality(cellchat, slot.name = "netP") 

#saveRDS(cellchat, "H:/LAB 20 IIT K/HIRN-PANC DB/HIRN updated/Working rds/HIRN_cellchat_states.detailed.conditon updated 123 JT.rds")


```

```{r}

cellchat <- readRDS("H:/LAB 20 IIT K/HIRN-PANC DB/HIRN updated/Working rds/HIRN_cellchat_states.detailed JT.rds")
cellchat <- setIdent(cellchat , ident.use = "labels")

levels(cellchat@idents) <- c( "Hs-Beta 1", "Hs-Beta 2", "Hs-Beta 3", "Hs-Alpha 1", "Hs-Alpha 2", "Hs-Delta 1", "Hs-Delta 2", "Hs-Gamma", "Hs-Acinar","Hs-PDCs", "Hs-Activated PSCs", "Hs-Quiescent PSCs", "Hs-Vascular ECs", "Hs-Metabolically active ECs", "Hs-Proinflammatory ECs", "Hs-Immune regulatory ECs", "Hs-T cells","Hs-Granulocytes","Hs-Macrophages", "Hs-APCs")

groupSize <- as.numeric(table(cellchat@idents))
par(mfrow = c(1,2), xpd=TRUE)



tiff(file="H:/LAB 20 IIT K/M.TECH THESIS/HIRN Data/Sheets/Cellchat/Number of interactions.tiff",height = 12, width = 12, res = 1200, units = "in")
#n1 <- netVisual_circle(cellchat@net$count, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Number of interactions", top = 0.40)
n1
dev.off()


tiff(file="H:/LAB 20 IIT K/M.TECH THESIS/HIRN Data/Sheets/Cellchat/Interaction weights strength.tiff",height = 12, width = 12, res = 1200, units = "in")
n2 <- netVisual_circle(cellchat@net$weight, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Interaction weights", top = 0.40)
n2
dev.off()

```



```{r}

df.net <- subsetCommunication(cellchat)
unique(df.net$pathway_name)
```
 png(file="/home/aahm/Desktop/filename_heatmap.png")
 ht <- Heatmap(...)
 draw(ht)
 dev.off()

```{r}
levels_ordered <- c( "Hs-Beta 1", "Hs-Beta 2", "Hs-Beta 3", "Hs-Alpha 1", "Hs-Alpha 2", "Hs-Delta 1", "Hs-Delta 2", "Hs-Gamma", "Hs-Acinar","Hs-PDCs", "Hs-Activated PSCs", "Hs-Quiescent PSCs", "Hs-Vascular ECs", "Hs-Metabolically active ECs", "Hs-Proinflammatory ECs", "Hs-Immune regulatory ECs", "Hs-T cells","Hs-Granulocytes","Hs-Macrophages", "Hs-APCs")

#subset signaling pathways with ht <- netAnalysis_signalingRole_heatmap(cellchat, signaling = c("SOMATOSTATIN", "INSULIN"))


ht1 <- netAnalysis_signalingRole_heatmap(cellchat, pattern = "outgoing", )
ht1

ht2 <- netAnalysis_signalingRole_heatmap(cellchat, pattern = "incoming")
ht2

ht1+ht2

 tiff(file="H:/LAB 20 IIT K/M.TECH THESIS/HIRN Data/Sheets/Cellchat/HIRN_data outgoing signaling network.tiff",height = 8, width = 8, res = 1200, units = "in")
 draw(ht1)
 dev.off()
 
 
tiff(file="H:/LAB 20 IIT K/M.TECH THESIS/HIRN Data/Sheets/Cellchat/HIRN_data incoming signaling network.tiff",height = 8, width = 8, res = 1200, units = "in")
 draw(ht2)
 dev.off()
```




```{r}
selectK(cellchat, pattern = "incoming")
nPatterns = 3

cellchat <- identifyCommunicationPatterns(cellchat, pattern = "outgoing", k = nPatterns)
R1 <- netAnalysis_river(cellchat, pattern = "outgoing")
R1
ggsave(plot = R1, filename = "HIRN_data outgoing pattern river.tiff", path = "H:/LAB 20 IIT K/M.TECH THESIS/HIRN Data/Sheets/Cellchat/",height = 8, width = 16, device = "tiff", dpi = 600)


cellchat <- identifyCommunicationPatterns(cellchat, pattern = "incoming", k = nPatterns)
R2 <- netAnalysis_river(cellchat, pattern = "incoming")
R2
ggsave(plot = R2, filename = "HIRN_data incoming pattern river.tiff", path = "H:/LAB 20 IIT K/M.TECH THESIS/HIRN Data/Sheets/Cellchat/",height = 8, width = 16, device = "tiff", dpi = 600)


```

```{r}
netVisual_heatmap(cellchat, signaling = "INSULIN", color.heatmap = "Reds")
```

```{r}
cellchat <- computeNetSimilarity(cellchat, type = "functional")
cellchat <- netEmbedding(cellchat, type = "functional")
#> Manifold learning of the signaling networks for a single dataset
cellchat <- netClustering(cellchat, type = "functional")
#> Classification learning of the signaling networks for a single dataset
# Visualization in 2D-space
E1 <- netVisual_embedding(cellchat, type = "functional", label.size = 3.5)
ggsave(plot = E1, filename = "HIRN_data functional pathway similarity.tiff", path = "H:/LAB 20 IIT K/M.TECH THESIS/HIRN Data/Sheets/Cellchat/",height = 6, width = 8, device = "tiff", dpi = 600)

```

```{r}
cellchat <- computeNetSimilarity(cellchat, type = "structural")
cellchat <- netEmbedding(cellchat, type = "structural")
#> Manifold learning of the signaling networks for a single dataset
cellchat <- netClustering(cellchat, type = "structural")
#> Classification learning of the signaling networks for a single dataset
# Visualization in 2D-space
E2 <- netVisual_embedding(cellchat, type = "structural", label.size = 3.5)

ggsave(plot = E2, filename = "HIRN_data structural pathway similarity.tiff", path = "H:/LAB 20 IIT K/M.TECH THESIS/HIRN Data/Sheets/Cellchat/",height = 6, width = 8, device = "tiff", dpi = 600)

```

```{r}
d1 <- netAnalysis_dot(cellchat, pattern = "outgoing")
d2 <- netAnalysis_dot(cellchat, pattern = "incoming")

ggsave(plot = d1, filename = "HIRN_data netAnalysis dot pathway outgoing.tiff", path = "H:/LAB 20 IIT K/M.TECH THESIS/HIRN Data/Sheets/Cellchat/",height = 5, width = 9, device = "tiff", dpi = 600)

ggsave(plot = d2, filename = "HIRN_data netAnalysis dot pathway incoming.tiff", path = "H:/LAB 20 IIT K/M.TECH THESIS/HIRN Data/Sheets/Cellchat/",height = 5, width = 9, device = "tiff", dpi = 600)

saveRDS(cellchat, "H:/LAB 20 IIT K/HIRN-PANC DB/HIRN updated/Working rds/HIRN_cellchat_states.detailed JT.rds")
```

```{r}


writexl::write_xlsx(df.net, "H:/LAB 20 IIT K/M.TECH THESIS/HIRN Data/Sheets/Cellchat/df net subtype detailed.xlsx")
```

```{r}
pdf(file = "H:/LAB 20 IIT K/M.TECH THESIS/HIRN Data/Sheets/Cellchat/individual circle plots.pdf", width = 10, height = 10)

mat <- cellchat@net$weight
for (i in 1:nrow(mat)) {
  mat2 <- matrix(0, nrow = nrow(mat), ncol = ncol(mat), dimnames = dimnames(mat))
  mat2[i, ] <- mat[i, ]
  netVisual_circle(mat2, vertex.weight = groupSize, weight.scale = T, edge.weight.max = max(mat), title.name = rownames(mat)[i])
}

dev.off()
```

```{r}
df.net <- subsetCommunication(HIRN_cellchat_states.detailed.conditon)

```

